Linear vertical shear instability in astrophysical disks: a semi-numerical study

### 2014-12-16 linear_adia.tex
update adia fig

\begin{figure}
  \includegraphics[width=\linewidth]{figures/rate_theory_gmma}
  \caption{Growth rate of the fundamental VSI mode in vertically
    isothermal disks ($\Gamma=1$) subject to adiabatic perturbations,
    calculated in thin disk approximation from Eq. \ref{adia_disp}
    with $M=0$, $\epsilon=0.1$ and  
    $|q|=1$. Growth rates are shown as a function of the radial
    wavenumber for different values of the adiabatic index
    $\gamma$. For $\gamma\equiv 1$ the perturbations are isothermal
    and there is no vertical entropy gradient.\label{adia_growth}}  
\end{figure}

>>>>

\begin{figure}
  \includegraphics[width=\linewidth,clip=true,trim=0cm 1.75cm 0cm 0cm]{figures/rate_theory_om}
  \includegraphics[width=\linewidth,clip=true,trim=0cm 0cm 0cm 1cm]{figures/rate_theory_nu}
  \caption{Real frequency (top) and growth rate (bottom) of the fundamental VSI mode in vertically 
    isothermal disks ($\Gamma=1$) subject to adiabatic perturbations,
    calculated in thin disk approximation from Eq. \ref{adia_disp}
    with $M=0$, $\epsilon=0.1$ and  
    $|q|=1$. Frequencies are shown as a function of the radial
    wavenumber for different values of the adiabatic index
    $\gamma$. For $\gamma\equiv 1$ the perturbations are isothermal
    and there is no vertical entropy gradient.\label{adia_growth}}  
\end{figure}
